\cvsection{Experience}
\begin{cventries}
  \cventry
	{Student Developer} % Job title
	{Google Summer of Code} % Organization
	{Waterloo, Canada} % Location
	{May. 2018 - Present} % Date(s)    
    {
      \begin{cvitems}
        \item {Working with Peter Norvig (Director of Research at Google) to design and implement a student-instructor workflow for a new platform. This platform will host aima-exercises which will not appear in the fourth edition of the book Artificial Intelligence: A Modern Approach.}
      \end{cvitems}
    }
  \cventry
	{Graduate Research and Teaching Assistant} % Job title
	{University Of Waterloo} % Organization
	{Waterloo, Canada} % Location
	{Sept. 2017 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Part of the Human-Computer-Interaction lab in David R Cheriton School of Computer Science. My research is focused towards Conversational Agents and building Intelligent User Interfaces.}
        \item {I have also hold TA position for various courses (CS 330, CS 490, CS 349). My responsibilities include marking, proctoring, holding office hours (and occasionally filling a lecture if instructor is unavailable).}
      \end{cvitems}
    }
  \cventry
    {Software Engineer} % Job title
    {Compro Technologies} % Organization
    {New Delhi, India} % Location
    {Oct. 2014 - Aug. 2017} % Date(s)
    {
      \begin{cvitems}
        \item {I was part of the primary development team and worked on the full technological stack for web and mobile applications. I was involved in creating next generation e-learning products (e-reader, courseware) for better user engagement and achieve pure learning vision.}
      \end{cvitems} 
    }
  \cventry
    {Summer Student Intern} % Job title
    {CERN, GS-Scientific Information Service} % Organization
    {Geneva, Switzerland} % Location
    {June. 2014 - Aug. 2014} % Date(s)
    {
      \begin{cvitems}
        \item {Worked at 'Scientific Information Services' department(GS-SIS) to enrich exiting metadata with data from other libraries and integrate changes into the open source software 'invenio'. Updated metadata was made available on CDS (CERN Document Server) after the internship.}
      \end{cvitems}
    }
  \cventry
    {Research Scholar, SPARK} % Job title
    {CSIR-Fourth Paradigm Institute} % Organization
    {Bangalore, India} % Location
    {Aug. 2013 - Dec. 2013} % Date(s)
    {
      \begin{cvitems}
        \item {Worked with Dr Gopal Krishna Patra (Principal Scientist, CSIR 4PI) to create a secure cryptosystem inspired by chaos theory. This was a part of CSIR-SPARK (Student Program for Advancement in Research Knowledge).}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
\end{cventries}
