%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	\cvprojects
	{\begin{cvitems} % Description(s) of experience/contributions/knowledge
			\item {StoryKart: An educational platform to craft and share interactive stories. Includes insanely simple drag-drop interface with script-editor to create awesome stories.}
			\item {ComproDLS: A learning ecosystem containing experience-apps to create immersive learning experience. Includes learning analytics, social collaboration, competency based learning with adaptive personalizations.}
			\item {Tweebbles: Data-centric view of user tweets with beautiful visualizations. Allows generation of uber bubble clouds for user-specific tweets and perform live sentiment analysis of tweets from twitter streaming api.}
			\item {ChatJS: A prototype suite of integrated products for rapid communication on web applications. Empowers sales, marketing, and support teams to proactively engage with visitors via live chat.}
			\item {Cosmic Shooters: A cross-platform battle-ship game based on HTML5 Canvas which uses real-time bidirectional event-based communication via socket.io to share player positions.}
			\item {MarkdownJS: A Markdown parser focused on simplicity and easy extensibility.}
	\end{cvitems}
}
\end{cventries}

